\chapter{Introduction}

\section{Background and context}

In cities, traffic jams at stoplight intersections are a big problem that makes transportation systems work less well. More and more people moving into cities and more cars on the road make it even trickier to find ways to deal with this issue. We really need new and smart ideas to handle and improve the flow of traffic. Machine Learning (ML), a kind of technology that can predict things, makes up for a good solution. It can help make traffic management at stoplight intersections better by telling us what might happen ahead of time. 

Lots of people living in cities and more cars on the roads mean more traffic jams at stoplights (traffic signals). The usual systems we use to control traffic struggle to adapt to these changes and don't always work well. That's why we need a different approach. Machine learning, which can learn from past data, seems like a good fit. By looking at how traffic behaved before, it can predict how it might behave in the future at stoplight intersections. Making decisions about traffic in real-time is super important, and machine learning helps us do it fast and smart. So, looking into how machine learning can predict traffic at stoplight intersections is important to create smarter and better ways to handle traffic in our cities. Various methodologies of machine learning and deep learning are already in use from which we can be able to draw some valuable insights on what can be the best option for us to implement for our problem statement.

Technology used for this project: predominantly for this project python with its libraries has been used for understanding the neural networks and modelling. PyTorch functions and its application will be discussed followed by the mathematical interpretation behind the same.
\clearpage
\section{Research questions}

\begin{enumerate}[label=\textbf{RQ\arabic*:}]
    \item What are the use cases in which machine learning model can be utilized in traffic prediction for context where some level of history of congestion at a point in time is known?
   
   
    
    \item What is the algorithm to train the machine learning model to predict the outcome for a time-series data way ahead in time?

  \end{enumerate}
